\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

%%%-----------------------------------------------------------------
%: fig:motion_task
%%%-----------------------------------------------------------------
\begin{figure}%[h!]%[ht!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/motion_task.pdf}
    \caption{
        {\bf - Motion Detection Task.} \textit{(Left)}~We use large natural images ($256\times256$) in which an aperture ($64\times64$) extracts a cropped image around the view axis. To mimic the effect of a saccadic eye movement, the view axis moves according to a step-wise random walk. We show such a trajectory with a length of $128$ time steps (green line). \textit{(Right)}~Snapshots of the synthetic event stream at different time steps (start and end frames denoted by a white and black dot, respectively). The dynamics of the cropped image translated according to the trajectory as a function of time produces a naturalistic movie which is then transformed into an event-based representation. Mimicking the retina, this representation encodes proportional increases or decreases in luminance, i.e. ON (red) and OFF (blue) events, in each pixel of the image. In the lower left corner of the snapshots, the translation vector is shown in red as one of the possible classes of motion. Note the change in the direction of motion between the second and third image and that due to the aperture problem, contours parallel to the motion emit relatively less spikes.}
    \label{fig:motion_task}
\end{figure}
%%%-----------------------------------------------------------------
Once these eye trajectories are generated, we can apply them to a visual scene.  
For this purpose, we selected a database of $600$ natural images that were previously used to study the statistics of natural images~\citep{perrinet_edge_2015}. Note that these have been pre-processed to be in grayscale and to equalize (i.e., whiten) the energy in each frequency band. This process is known to occur in the retino-thalamic pathway~\citep{dan_efficient_1996}. These images are $256 \times 256$ in size, and we will extract sub-images of size $64 \times 64$ positioned around the center of gaze at each time step. We will discretize time in $1~\ms$ bins and produce movies of duration $N_T = 128~\ms$. To avoid boundary effects, we will randomly position the full trajectory in image space such that the subimage is translated using the position given by the trajectory at each time step without touching the borders. At each point in time, the translation is computed using a coordinate roll in the horizontal and vertical dimensions, followed by a sub-pixel translation defined in Fourier space~\citep{perrinet_sparse_2015}. Note that the magnitude of the displacement is relative to the time bin, and we have defined the unit velocity to correspond to a movement of one pixel per frame (i.e., per time bin).

>>>>

%%%-----------------------------------------------------------------
%: fig:motion_task
%%%-----------------------------------------------------------------
\begin{figure}%[h!]%[ht!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/motion_task.pdf}
    \caption{
        {\bf - Motion Detection Task.} \textit{(Left)}~We use large natural images ($256\times256$) in which an aperture ($64\times64$) extracts a cropped image around the view axis. To mimic the effect of a saccadic eye movement, the view axis moves according to a step-wise random walk. We show such a trajectory with a length of $128$ time steps (green line). \textit{(Right)}~Snapshots of the synthetic event stream at different time steps (start and end frames denoted by a white and black dot, respectively). The dynamics of the cropped image translated according to the trajectory as a function of time produces a naturalistic movie which is then transformed into an event-based representation. Mimicking the retina, this representation encodes proportional increases or decreases in luminance, i.e. ON (red) and OFF (blue) events, in each pixel of the image. In the lower left corner of the snapshots, the translation vector is shown in red as one of the possible classes of motions. Note the change in the direction of motion between the third and fourth image, and also that due to the aperture problem, contours parallel to the motion emit relatively less spikes.}
    \label{fig:motion_task}
\end{figure}
%%%-----------------------------------------------------------------
Once these eye trajectories are generated, we can apply them to a visual scene.  
For this purpose, we selected a database of $600$ natural images that were previously used to study the statistics of natural images~\citep{perrinet_edge_2015}. Note that these have been pre-processed to be in grayscale and to equalize (i.e., whiten) the energy in each frequency band. This process is known to occur in the retino-thalamic pathway~\citep{dan_efficient_1996}. These images are $256 \times 256$ in size, and we will extract sub-images of size $64 \times 64$ positioned around the center of gaze at each time step. We will discretize time in $1~\ms$ bins and produce movies of duration $N_T = 128~\ms$. To avoid boundary effects, we will randomly position the full trajectory in image space such that the subimage is translated using the position given by the trajectory at each time step without touching the borders. At each point in time, the translation is computed using a coordinate roll in the horizontal and vertical dimensions, followed by a sub-pixel translation defined in Fourier space~\citep{perrinet_sparse_2015}. Note that the magnitude of the displacement is relative to the time bin, and we have defined the unit velocity to correspond to a movement of one pixel per frame (i.e., per time bin).
